Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2014-10-01 exp1/present2013.tex
describe Lenth
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@767 43ef1190-90fd-4dd7-a769-d0121f02b80e

% TODO: My factors

@@

    \begin{itemize}
    \item When experimental economy is important,
    \item DoE theory offers extensive facilities for running a
      fraction of the runs ($2^{n-1}$ etc).
    \item The price is of smaller experiments is explanatory power.
    \end{itemize}
  \end{itemize}
\end{frame}
\note{
  \begin{itemize}
  \item These are called fractional experiments, and come in two
    shapes, full, as we have seen a design matrix of, and fractional. 
  \item With fractional, we trade explanatory power for economy.
  \item We first study a full factorial, in the paper we have three
    fractional, we shall see the final fractional
  \end{itemize}
}

@@

\note{
  \begin{itemize}
% TODO: Lenth
  \item Those that are deemed significant are labelled.
  \item Don't worry about the axes
  \item Yes, the Implementation is better, we knew that, 
  \item Interactions with Implement with joins are
    naturally strong
  \item ``Union'', ``Optional'' and ``Lang'' demanding things
  \item ``BGPComp:Lang'' and ``Lang:Union'' interactions might be due
    to that many more triples need to be searched for a language tag
    in one of the levels of the interacting factors.
  \item But what about ``Implement::TripleC''? Leave that hanging for
    a bit.
  \item We want to do a hypothesis test
  \item Two factors do not contribute significantly to the variation
    ``Range'' and ``Machine''.
  \end{itemize}
}

@@

% Experimental economy

>>>>

@@

    \begin{itemize}
    \item When experimental economy is important,
    \item DoE theory offers extensive facilities for running a
      fraction of the runs ($2^{n-1}$ etc).
    \item The price is of smaller experiments is explanatory power.
    \end{itemize}
  \end{itemize}
\end{frame}
\note{
  \begin{itemize}
  \item These are called fractional experiments, and come in two
    shapes, full, as we have seen a design matrix of, and fractional. 
  \item With fractional, we trade explanatory power for economy.
  \item We first study a full factorial, then three fractional 
  \end{itemize}
}

@@

\note{
  \begin{itemize}
  \item Significance is based on Lenth's method, where he computes a
    pseudo-standard error, since we have only one replicate. This is
    based on computing the median of the absolute effects, and then
    again the median of the smallest effects.
  \item Those that are deemed significant are labelled.
  \item Don't worry about the axes
  \item Yes, the Implementation is better, we knew that, 
  \item Interactions with Implement with joins are
    naturally strong
  \item ``Union'', ``Optional'' and ``Lang'' demanding things
  \item ``BGPComp:Lang'' and ``Lang:Union'' interactions might be due
    to that many more triples need to be searched for a language tag
    in one of the levels of the interacting factors.
  \item But what about ``Implement::TripleC''? Leave that hanging for
    a bit.
  \item We want to do a hypothesis test
  \item Two factors do not contribute significantly to the variation
    ``Range'' and ``Machine''.
  \end{itemize}
}

@@
